Predicting I/O performance in HPC using artificial neural networks

### 2016-07-08 Paper/paper.tex
abgeschickte Version

\usepackage{amssymb}
\usepackage{csvsimple}
\usepackage{blindtext}

@@

	\title{Predicting I/O performance in HPC using Artificial Neural Networks}

@@

	As expected, sequential file accesses are on average much faster than random accesses especially for the reading case, also random reads are slower than writes. In Figure \ref{correlations}, we consider the correlations between file access parameters and the resulting access time, a strong correlation can be exploited for access time prediction.
	\tab{correlations}{Correlations between file access parameters and access time}{
		\centering
		\scriptsize
		\begin{tabular}{|r|r|r|}\hline%
			Attribute & Sequential access pattern & Random access pattern\\\hline\hline
			\csvreader[late after line=\\\hline]%
			{src/data_summary_korrelationen.csv}{Attribut=\Attribut,seq = \seq, rnd = \rnd}%
			{\Attribut & \seq &\rnd}%
		\end{tabular}
	}

>>>>

\usepackage{amssymb}
\usepackage{csvsimple}

@@

	\title{Predicting I/O performance in HPC using artificial neural networks}

@@

	As expected, sequential file accesses are on average much faster than random accesses especially for the reading case, also random reads are slower than writes. In Figure \ref{correlations}, we consider the correlations between file access parameters and the resulting access time, a strong correlation can be exploited for access time prediction.
	\tab{correlations}{Correlations between file access parameters and access time}{
		\centering
		\scriptsize
		\begin{tabular}{|r|r|r|}\hline%
			Attribute & Sequential access pattern & Random access pattern\\\hline\hline
			\csvreader[late after line=\\\hline]%
			{src/data_summary_correlations.csv}{Attribut=\Attribut,seq = \seq, rnd = \rnd}%
			{\Attribut & \seq &\rnd}%
		\end{tabular}
	}
